\documentclass[a4paper, 12]{article}
	\begin{document}
		
		\title{Bomberman Game Design Document}
		\author{Jerry Hu, $6229077$ \\ Maaike Koninx, $6303919$}
		\date{\today}	
		\maketitle
		
		\section{Game Description}
			Bomberman is an action strategy game. The goal of the game is for the player to eliminate enemies by placing down bombs. Bombs will explode in several directions after an amount of time. The game is played on a 15 x 13 or 17 x 15 grid. 
		
		\subsection{Player}
		The player will control a character which can walk around the map and place bombs. The player can move the character by using WASD or arrows of a keyboard. By pressing spacebar he/she can plant a bomb. 
		\subsection{Map}			
			The map is a grid that contains several blocks which can be either destructible or indestructible by bombs. The indestructible blocks are placed every two blocks on the field. The destructible blocks are randomly placed on the map. The player and his/her enemies will first have to destroy several blocks to reach each other. Destructible blocks can also drop power-ups which enhances the abilities of a player. 
		
		\subsection{Enemies}
		
		Enemies in the game will move around the map randomly. The enemy can be defeated by hitting it with an explosion from a bomb. When a player intersects with an enemy he/she will lose health. The enemies themselves can not plant bombs.
		
		\subsection{Power-ups}
		Blocks can drop several power-ups:
		\begin{itemize}
			\item Speed boost, enhances the movement speed of the player by 2
			\item Bomb Amount, raises the amount of bombs that a player can place simultaneously by 1
			\item Explosion size, enhances the explosion size of a bomb by 2
		\end{itemize}

		
		\subsection{Animations}
		Several objects will be animated during gameplay:
		\begin{itemize}
			\item Player movement
			\item Enemy movement
			\item Bomb explosion
		\end{itemize}	
		
		\section{Data types and Typeclasses}
		The game will have several data types and typeclasses.
	
		
		\subsection{Data types}
		The following data types are described by their names and attributes
			\begin{itemize}
				\item Player
					\begin {itemize}
						\item playerPosition :: (Int,Int)
						\item health :: Int
						\item moveSpeed :: Float
						\item direction :: Direction (Up | Down | Left | Right)
						\item sprite :: Sprite
					\end{itemize}
				\item Bomb 
					\begin{itemize}
						\item explosionRadius :: Int
						\item explosionTime :: Float
						\item bombPosition :: (Int,Int)
					\end{itemize}
				\item Grid :: [Field]
				\item Field 
					\begin{itemize}
						\item fieldPosition :: (Int, Int)
						\item gameObject :: GameObject
					\end{itemize}					
				\item Powerup: SpeedBoost | DropAmount | 										ExplosionSize
				\item GameObject :: Block | IndestructableBlock | Empty
				\item GameState: Player, [Player], Grid, Paused
			\end{itemize}
				
		\subsection{Typeclasses}
			\begin{itemize}
				\item Positioned, type that has a position
				\item Movable, type that can move into a direction
				\item Living, type that can either be dead or alive
				\item Destructible, item that can be destroyed by explosions
			\end{itemize}
		
		\end{document}			
	